%!TEX root = art-in-machine-learning.tex

\section{Audio Data}
\label{sec:music}

Common machine learning tasks which involve audio data are speech recognition,
speaker identification, identification of songs. This leads to some
less-common, but interesting topics: The composition of music, the synthezation
of audio as art. While the composition might be considered in
\cref{sec:text-generation}, we will now investigate the work which was done in
audio synthezation.

\subsection{GRUV}

Recurrent neural networks --- \gls{LSTM} networks, to be exact --- are used
in~\cite{nayebigruv} together with \gls{GRU} to build a network which can be
trained to generate music. Instead of taking notes directly or MIDI files,
Nayebi and Vitelli took raw audio waveforms as input. Those audio waveforms are
feature vectors given for time steps $0, 1, \dots, t-1, t$. The network is
given those feature vectors $X_1, \dots, X_t$ and has to predict the following
feature vector $X_{t+1}$. This means it continues the music. As the input is
continous, the problem was modeled as a regression task. \Gls{DFT} was used on
chunks of length $N$ of the music to obtain features in the frequency domain.


\subsection{Audio Synthezation}
TODO: \href{http://gitxiv.com/posts/dQxgWraeWgvpKJXLG/musical-audio-synthesis-using-autoencoding-neural-nets}{http://gitxiv.com/posts/dQxgWraeWgvpKJXLG/musical-audio-synthesis-using-autoencoding-neural-nets}

\href{http://gitxiv.com/posts/kZz9PCRcktdYSrWnp/deephear-composing-and-harmonizing-music-with-neural}{http://gitxiv.com/posts/kZz9PCRcktdYSrWnp/deephear-composing-and-harmonizing-music-with-neural}

\href{http://gitxiv.com/posts/QP262Yfc7mZCDocPe/composing-music-with-recurrent-neural-networks}{http://gitxiv.com/posts/QP262Yfc7mZCDocPe/composing-music-with-recurrent-neural-networks}

\href{http://gitxiv.com/posts/WEoQCj8hxHz6vPxe6/gruv-algorithmic-music-generation-using-recurrent-neural}{http://gitxiv.com/posts/WEoQCj8hxHz6vPxe6/gruv-algorithmic-music-generation-using-recurrent-neural}

\subsection{0music}
TODO: \href{https://en.wikipedia.org/wiki/0music}{https://en.wikipedia.org/wiki/0music}

\href{https://www.youtube.com/watch?v=-a3QsSDfUsA}{https://www.youtube.com/watch?v=-a3QsSDfUsA}


\subsection{AARON}

TODO

\enquote{AARON is a software program written by artist Harold Cohen that creates original artistic images.} - source: en-wiki

TODO: \href{http://artsites.ucsc.edu/faculty/cope/experiments.htm}{http://artsites.ucsc.edu/faculty/cope/experiments.htm}


\subsection{The Generative Electronica Research Project}

\href{http://metacreation.net/gerp/}{http://metacreation.net/gerp/}
